\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/background.tex
Spelling

\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the station to initiate communication. This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station. Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}. In principle \scheme can use any of these mechanisms for registration, but in our prototype we used the HTTPS request body as it offers the greatest flexibiity for the amount of data that can be sent with the registration.

>>>>

\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the station to initiate communication. This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station. Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}. In principle \scheme can use any of these mechanisms for registration, but in our prototype we used the HTTPS request body as it offers the greatest flexibility for the amount of data that can be sent with the registration.

### 2019-02-16 paper/paper.tex
Spelling

TapDance was designed for ease of deployment.
Instead of in-line network devices required by earlier schemes, it
calls for only a passive tap.
This ``on-the-side'' approach, though much friendlier from an ISP's
perspective, leads to major challenges when interposing in an ongoing
client-to--decoy connection:
\begin{compactitem}
\item Implementation is complex and error-prone, requiring kernel
  patches or a custom TCP stack.
\item To avoid detection, the system must carefully mimmick
  subtle features of each decoy's TCP and TLS behavior.
\item The architecture cannot resist active probing attacks, where the
  censor sends specially crafted packets to determine whether a
  suspected connection is using TapDance.
\item Interactions with the decoy's network stack limit the length and
  duration of each connection, forcing TapDance to multiplex
  long-lived proxy connections over many shorter decoy
  connections. This adds overhead and creates a traffic pattern
  that is challenging to conceal.
\end{compactitem}

@@

Clients can register intent to use the proxy in several covert ways. For
instance, they could use email or other existing intermitently available proxies
to register. In this section, we use a form of Refraction Networking similar to
TapDance to register directly with the station.

@@

\paragraph{Popular sites.}
An alternative strategy is to use popular sites, such as those from the Alexa
top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
sites that are obviously not hosted in the phantom host address range, such as
large companies that run their own datacenters and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a phantom host corresponds to a domain's IP.

@@

Client begins registation by establishing TLS connection
to one of the reachable websites,
path to which passes by our tap.
Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance14} to manupulate
plaintext of a first application data HTTP request
to get desired ciphertext,
and exchange keys with the station.
After client writes Elligator-encoded~\cite{elligator} representative into the ciphertext at a static offset of 92 bytes from the end,
that could be decoded using station's private key,
to negotiate a 32 byte Eligator-encoded~\cite{elligator} shared secret between the client and the station.
That shared secret is used as a seed of SHA-256 based key derivation function (HKDF),
allowing station and client to derive an unlimited amount of shared secrets.

Elligator representative on the wire is immidiately followed by a 6 bytes long AES-GCM-encrypted
fixed size payload(FSP), that holds flags and the size of the variable size payload(VSP).
IV and key for encrypted of both FSP and VSP will be derived from HKDF.
Once FSP is decrypted and the size of VSP is known, station can decrypt the VSP as well.
VSP itself is a protobuf, which allows us to easily change the contents of VSP without risk of version mismatch, and currently contains 3 fields: version of configuration(which includes list of decoys), SNI of mask site, and a presumably blocked target host that client would like to get connected to.

@@

\subsection{Application phase}
Client and station will use HKDF to derive 16 random bytes and use them to
agree on a phantom host IP address, by applying a simple selection algorithm.
Algorithm is as follows: first, flatten a list of pre-shared avaliable IP
addresses in various subnets into a single indexed list, then make a 128-bit
integer out of 16 random bytes and divide it by the length
of the flattened list, and use the remainder of this division as an index
of the list to pick an IP address.

>>>>

TapDance was designed for ease of deployment.
Instead of in-line network devices required by earlier schemes, it
calls for only a passive tap.
This ``on-the-side'' approach, though much friendlier from an ISP's
perspective, leads to major challenges when interposing in an ongoing
client-to--decoy connection:
\begin{compactitem}
\item Implementation is complex and error-prone, requiring kernel
  patches or a custom TCP stack.
\item To avoid detection, the system must carefully mimic
  subtle features of each decoy's TCP and TLS behavior.
\item The architecture cannot resist active probing attacks, where the
  censor sends specially crafted packets to determine whether a
  suspected connection is using TapDance.
\item Interactions with the decoy's network stack limit the length and
  duration of each connection, forcing TapDance to multiplex
  long-lived proxy connections over many shorter decoy
  connections. This adds overhead and creates a traffic pattern
  that is challenging to conceal.
\end{compactitem}

@@

Clients can register intent to use the proxy in several covert ways. For
instance, they could use email or other existing intermittently available proxies
to register. In this section, we use a form of Refraction Networking similar to
TapDance to register directly with the station.

@@

\paragraph{Popular sites.}
An alternative strategy is to use popular sites, such as those from the Alexa
top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
sites that are obviously not hosted in the phantom host address range, such as
large companies that run their own data centers and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a phantom host corresponds to a domain's IP.

@@

Client begins registration by establishing TLS connection
to one of the reachable websites,
path to which passes by our tap.
Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance14} to manipulate
plaintext of a first application data HTTP request
to get desired ciphertext,
and exchange keys with the station.
After client writes Elligator-encoded~\cite{elligator} representative into the ciphertext at a static offset of 92 bytes from the end,
that could be decoded using station's private key,
to negotiate a 32 byte Elligator-encoded~\cite{elligator} shared secret between the client and the station.
That shared secret is used as a seed of SHA-256 based key derivation function (HKDF),
allowing station and client to derive an unlimited amount of shared secrets.

Elligator representative on the wire is immediately followed by a 6 bytes long AES-GCM-encrypted
fixed size payload(FSP), that holds flags and the size of the variable size payload(VSP).
IV and key for encrypted of both FSP and VSP will be derived from HKDF.
Once FSP is decrypted and the size of VSP is known, station can decrypt the VSP as well.
VSP itself is a protobuf, which allows us to easily change the contents of VSP without risk of version mismatch, and currently contains 3 fields: version of configuration(which includes list of decoys), SNI of mask site, and a presumably blocked target host that client would like to get connected to.

@@

\subsection{Application phase}
Client and station will use HKDF to derive 16 random bytes and use them to
agree on a phantom host IP address, by applying a simple selection algorithm.
Algorithm is as follows: first, flatten a list of pre-shared available IP
addresses in various subnets into a single indexed list, then make a 128-bit
integer out of 16 random bytes and divide it by the length
of the flattened list, and use the remainder of this division as an index
of the list to pick an IP address.

### 2019-02-16 paper/related.tex
Spelling

In practice, deployment of refraction networking has so far been at access, rather than transit ISPs~\cite{frolov2017isp}. This may be in part because a transit ISP has a large number of routers and points-of-presence, significantly raising the costs of deployment~\cite{devil-details}.\footnote{We
note that Gosain et al.~\cite{devil-details} use an estimate of \$885\,000 USD/proxy, while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment using commodity hardware that cost only several thousand dollars.} Likewise, we expect \scheme to use address space announced by the ISP, rather than addresses relayed by it, which mitigates routing-based attacks. Depending on the size of the ISP, however, a censor may decide to block the entirety of its address space, which would incur smaller collateral damage than blocking all addresses seen by a transit ISP.

@@

Traditionally, proxies deployed for censorship are eventually identified and blocked by the censor. Several proposals have been made to carefully control  the distribution of proxy addresses, using social connections and reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this information secret is challenging; additonally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations. \scheme further this goal by creating a large number of destinations out of the dark space. A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations. CensorSpoofer, however, could only send information in one direction---to the client---and had to rely on a separate out-of-band channel for client-to-proxy communication. As an alternative approach, FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to run Flash- or WebRTC-based proxies within their browser to allow censored users to connect to the Tor network with the potential to greatly increase the number. In practice, these proxies served a very small number of users, as compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}

>>>>

In practice, deployment of refraction networking has so far been at access, rather than transit ISPs~\cite{frolov2017isp}. This may be in part because a transit ISP has a large number of routers and points-of-presence, significantly raising the costs of deployment~\cite{devil-details}.\footnote{We
note that Gosain et al.~\cite{devil-details} use an estimate of \$885,000/proxy, while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment using commodity hardware that costs only several thousand dollars.} Likewise, we expect \scheme to use address space announced by the ISP, rather than addresses relayed by it, which mitigates routing-based attacks. Depending on the size of the ISP, however, a censor may decide to block the entirety of its address space, which would incur smaller collateral damage than blocking all addresses seen by a transit ISP.

@@

Traditionally, proxies deployed for censorship are eventually identified and blocked by the censor. Several proposals have been made to carefully control  the distribution of proxy addresses, using social connections and reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this information secret is challenging; additionally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations. \scheme further this goal by creating a large number of destinations out of the dark space. A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations. CensorSpoofer, however, could only send information in one direction---to the client---and had to rely on a separate out-of-band channel for client-to-proxy communication. As an alternative approach, FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to run Flash- or WebRTC-based proxies within their browser to allow censored users to connect to the Tor network with the potential to greatly increase the number. In practice, these proxies served a very small number of users, as compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}
